Double-Stranded Differential Evolution and Particle Swarm Optimization with LibreOffice Nonlinear Programming Solver\thanks{Supported by Velbazhd Software LLC.}

### 2024-02-02 Double-Stranded-Differential-Evolution-and-Particle-Swarm-Optimization-with-LibreOffice-Nonlinear-Programming-Solver/paper.tex
Some more text has been added.

>>>>

In conclusion, enhancing population-based algorithms inspired by DNA in LibreOffice Calc can potentially enhance problem-solving efficiency through evolutionary optimization. This adaptation can prove especially advantageous for resource-limited instances of LibreOffice Calc, empowering it to execute intricate tasks with increased speed and precision. For future investigations, exploring additional benchmark functions and evaluating performance on various mobile hardware platforms could be pursued.
